---
title: "Midterm project"
output: html_document
date: 10/23/2023
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}

file_path <- "C:\\Users\\mrani\\Downloads\\newexercise_dataset.csv"

df <- data.frame(read.csv(file_path))

# Examine the structure of the dataset
str(df)

```


```{r}

# Converting chr to factor
df$Exercise <- as.factor(df$Exercise)
df$Gender <- as.factor(df$Gender)
df$Weather.Conditions <- as.factor(df$Weather.Conditions)
str(df)

```


```{r}
summary(df)
```


```{r}
# NA values

paste("The NA's in the dataset is:",sum(is.na(df)))

```
```{r}

# Creating a new variable BMI.Classification
df$BMI.Classification <- ifelse(df$BMI < 18.5, "Underweight",
                                ifelse(df$BMI < 25, "Healthy weight",
                                       ifelse(df$BMI < 30, "Overweight", "Obesity")))

# Creating a new variable 'Intensity' based on Exercise.Intensity values
df$Intensity <- ifelse(df$Exercise.Intensity < 3, "Low Intensity",
                      ifelse(df$Exercise.Intensity < 6, "Medium Intensity", "High Intensity"))

# Checking the first few rows of the updated dataframe
head(df)


```
## This code creates new variables 'BMI.Classification' and 'Intensity' based on conditions and checks the first few rows of the updated dataset.


```{r}
# This code generates a histogram with a KDE (Kernel Density Estimation) overlay, showing the age distribution by gender.

library(ggplot2)

ggplot(df, aes(x = Age, fill = Gender)) +
  geom_histogram(binwidth = 2, alpha = 0.5, color = "black", aes(group = Gender)) +
  stat_density(geom = "line", aes(color = Gender, group = Gender)) +
  labs(title = "Age distribution with KDE", x = "Age") +
  theme_minimal()
```
```{r}
# This code creates a histogram to visualize the relationship between exercise intensity and calories burned.

exercise_calories <- ggplot(df, aes(x = Intensity, y = Calories.Burn)) +
  geom_histogram(stat = 'identity', fill = 'blue', color = 'grey') +
  labs(title = 'Exercise Intensity vs Calories Burn', x = 'Intensity', y = 'Calories Burn') +
  theme_minimal()

print(exercise_calories)

```
```{r}
# Age vs. Calories Burn

ggplot(df, aes(x = Age, y = Calories.Burn)) +
  geom_point() +
  labs(title = "Age vs. Calories Burn", x = "Age", y = "Calories Burn") +
  theme_minimal()

```
```{r}
# Gender vs. Exercise variety
library(dplyr)

df %>%
  group_by(Gender, Exercise) %>%
  summarise(Count = n()) %>%
  ggplot(aes(x = Exercise, y = Count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Gender Differences in Exercise Variety", x = "Exercise", y = "Count") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))

```

```{r}
# Indoor vs. Outdoor Exercises by Weather
library(tidyr)

df %>%
  group_by(Weather.Conditions, Exercise) %>%
  summarise(Count = n()) %>%
  pivot_wider(names_from = Weather.Conditions, values_from = Count, values_fill = 0) %>%
  ggplot(aes(x = Exercise, y = `Sunny`, fill = `Cloudy`)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Indoor vs. Outdoor Exercises by Weather", x = "Exercise", y = "Count") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))


```

## SMART Questions

### Q1: How do age, actual weight, and duration collectively influence the relationship between exercise intensity and calorie burn?

```{r Q1}
library(ggplot2)

ggplot(df, aes(x = Intensity, y = Calories.Burn, size = Age, color = Actual.Weight, alpha = Duration)) +
  geom_point() +
  scale_color_continuous() +
  scale_alpha_continuous(range = c(0.2, 0.8)) +
  labs(title = "Influence of Age, Actual Weight, and Duration on Exercise Intensity and Calorie Burn",
       x = "Exercise Intensity", y = "Calories Burn") +
  theme_minimal()

```

### Q2: Can we establish a time based trend in the dataset, such as changes in exercise preferences,calorie expenditure, or weight measurements over time?

```{r Q2}

exercise_trend <- df %>%
  group_by(Exercise, Age) %>%
  summarise(Count = n())

ggplot(exercise_trend, aes(x = Age, y = Count, color = Exercise)) +
  geom_line() +
  labs(title = "Trend in Exercise Preferences Over Time", x = "Age", y = "Count") +
  theme_minimal()


```

### Q3: Do males and females exhibit different patterns in terms of exercise variety?

```{r Q3}

df %>%
  group_by(Gender, Exercise) %>%
  summarise(Count = n()) %>%
  ggplot(aes(x = Exercise, y = Count, fill = Gender)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Gender Differences in Exercise Variety", x = "Exercise", y = "Count") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))


```

### Q4: Are there exercises more commonly performed indoors or outdoors, depending on the weather?

```{r Q4}

df %>%
  group_by(Weather.Conditions, Exercise) %>%
  summarise(Count = n()) %>%
  pivot_wider(names_from = Weather.Conditions, values_from = Count, values_fill = 0) %>%
  ggplot(aes(x = Exercise, y = `Sunny`, fill = `Cloudy`)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Indoor vs. Outdoor Exercises by Weather", x = "Exercise", y = "Count") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))


```

### Q5: Can the combination of heart rate and BMI be used to determine the optimal exercise duration for achieving dream weight?

```{r Q5}

ggplot(df, aes(x = Heart.Rate, y = BMI, color = Duration)) +
  geom_point() +
  labs(title = "Heart Rate vs. BMI (Color: Duration)", x = "Heart Rate", y = "BMI") +
  theme_minimal()


```

### Q6: How closely do individuals' dream weights align with their actual weights?

```{r Q6}

ggplot(df, aes(x = Dream.Weight, y = Actual.Weight)) +
  geom_point() +
  labs(title = "Dream Weight vs. Actual Weight", x = "Dream Weight", y = "Actual Weight") +
  theme_minimal()


```

