---
title: "Final_Yash"
output: html_document
date: "2023-10-23"
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing Required Packages

```{r Packages}
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("corrplot")

library(ggplot2)
library(dplyr)
library(corrplot)

```

## Data Preprocessing

For the data preprocessing part, we will do three things for now: 1. Load the Dataset 2. Check for Missing Values 3. Check Variable Datatypes & Typecast if necessary

```{r Loading dataset}
#setwd = "C:\\Users\\YASH KATTIMANI\\Downloads"
df = read.csv("newexercise_dataset.csv")
str(df)
```

```{r Check for Missing Values}
null_values <- sum(is.na(df))
print(null_values)
```

Turns out there are 0 null values, so we can go ahead without having to worry about this aspect.

```{r Typecasting}
#converting exercise from char to factor
df$Exercise <- as.factor(df$Exercise)
df$Gender <- as.factor(df$Gender)
df$Weather.Conditions <- as.factor(df$Weather.Conditions)
```

## Deep Dataset Analysis

Frequency of different Exercises

```{r Frequency of different Exercises}
library(ggplot2)
exercise_count <- ggplot(df,aes(x= Exercise,fill = Exercise))+
  geom_bar()+
  labs(title ="Distribution of Exercise", x = "Exercise", y = "Count" )+
  theme(axis.text.x = element_text(angle = 75,hjust = 1))+
  scale_fill_manual(values = rainbow(length(unique(df$Exercise))))
print(exercise_count)

```

Classification of BMI values to 4 different categories

```{r Classification of BMI values to 4 categories}
# Creating a new variable BMI.Classification based on BMI values
df$BMI.Classification <- ifelse(df$BMI < 18.5, "Underweight",
                                ifelse(df$BMI < 25, "Healthy weight",
                                       ifelse(df$BMI < 30, "Overweight", "Obesity")))

head(df)
```

Classification of Levels of Intensity based on Intensity values

```{r Classification of Levels of Intensity}
# Creating a new variable 'Intensity' based on Exercise.Intensity values
df$Intensity <- ifelse(df$Exercise.Intensity < 3, "Low Intensity",
                      ifelse(df$Exercise.Intensity < 6, "Medium Intensity", "High Intensity"))

# View the first few rows of the updated dataframe to verify the new variable
head(df)
```

Converting Heart rate to different levels "Low", "Moderate", "Elevated", "High", "Very High"

```{r Converting Heart rate to different levels}
breaks <- c(0, 100, 120, 140, 160, Inf)  # Customizing the breaks requirements
labels <- c("Low", "Moderate", "Elevated", "High", "Very High")

# Use the cut function to categorize Heart Rate into levels
df$HeartRateLevel <- cut(df$Heart.Rate, breaks = breaks, labels = labels, right = FALSE)
```

## Analysis of Age

📌Age analysis shows that men are more active until the age of 28, then women dominate. In addition, there are a large number of people over the age of 60.

```{r}
# Create a density plot with KDE
density_plot <- ggplot(df, aes(x = Age, fill = Gender, color = Gender)) +
  geom_density(alpha = 0.5) +
  labs(title = "Age distribution", x = "Age") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "red")) +
  scale_color_manual(values = c("blue", "red"))

print(density_plot)
```

```{r}
# Load the ggplot2 library
library(ggplot2)

# Create a histogram with ggplot2
hist_plot <- ggplot(df, aes(x = Age)) +
  geom_histogram(binwidth = 5, fill = "lightblue", color = "black") +
  labs(title = "Distribution of Age", x = "Age", y = "Count") +
  theme_minimal()

# Calculate the percentage of each bin and add percentage labels
hist_plot <- hist_plot +
  stat_bin(
    binwidth = 5, 
    geom = "text", 
    aes(label = scales::percent(..count.. / sum(..count..))),
    position = position_stack(vjust = 0.5)
  )

# Display the histogram plot
print(hist_plot)
```

### Analysis of BMI

Q)  Can the combination of heart rate and BMI be used to determine the optimal exercise duration for achieving dream weight?

```{r Smart Question 2}
ggplot(df, aes(y=Heart.Rate, x=BMI, color= BMI.Classification)) +
  geom_point() +
  ggtitle("Heart Rate and BMI vs Exercise Duration for Achieving Dream Weight")
```

```{r Plot for classification of BMI values to 4 categories}
library(ggplot2)

# Create a bar plot
bmi_bar_plot <- ggplot(df, aes(x = BMI.Classification, fill = BMI.Classification)) +
  geom_bar() +
  labs(title = "BMI Classification", x = "Classification", y = "Count") +
  scale_fill_manual(values = c(
    "Underweight" = "red",
    "Healthy weight" = "lightgreen",
    "Overweight" = "maroon",
    "Obesity" = "orange"
  )) +
  theme_minimal()

# Calculate and add percentage labels to each bar
bmi_bar_plot <- bmi_bar_plot +
  geom_text(
    aes(label = scales::percent(..count.. / sum(..count..)),
        y = ..count..,
        group = BMI.Classification),
    stat = "count",
    vjust = -0.5,  # Adjust the vertical position of labels
    hjust = 0.5,   # Center the labels horizontally
    position = position_stack(vjust = 0.5)
  )

# Display the bar plot
print(bmi_bar_plot)

```

```{r}
# Calculating the distribution of BMI classifications
bmi_class_counts <- table(df$BMI.Classification)

# Calculating the percentages
bmi_class_percentages <- prop.table(bmi_class_counts) * 100

# Create a pie chart
pie(bmi_class_counts, labels = paste(names(bmi_class_counts), "(", round(bmi_class_percentages, 1), "%)"), col = c("red", "green", "blue"))
title("Distribution by BMI Classification")
```

```{r}
# Calculating the distribution of BMI classifications
#bmi_class_counts <- table(df$BMI.Classification)

# Calculating the percentages
#bmi_class_percentages <- prop.table(bmi_class_counts) * 100

# Create a pie chart
#pie(bmi_class_counts, labels = paste(names(bmi_class_counts), "(", round(bmi_class_percentages, 1), "%)"), col = c("red", "green", "blue"))
#title("Distribution by BMI Classification")
```

```{r}
countplot <- ggplot(df, aes(x = Exercise, fill = BMI.Classification)) +
  geom_bar(position = "dodge") +
  labs(title = "Exercise by BMI Classification", x = "Exercise", y = "Count") +
  scale_fill_manual(values = c("Underweight" = "yellow","Overweight" = "red", "Obesity" = "green", "Healthy weight" = "blue")) +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))

print(countplot)

```

```{r}
library(ggplot2)

# Create a bar plot
bar_plot <- ggplot(df, aes(x = Exercise, fill = BMI.Classification)) +
  geom_bar(position = "dodge") +
  labs(title = "Exercise by BMI Classification", x = "Exercise", y = "Count") +
  scale_fill_manual(values = c(
    "Underweight" = "yellow",
    "Overweight" = "red",
    "Obesity" = "green",
    "Healthy weight" = "blue"
  )) +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))

# Create a box plot
box_plot <- ggplot(df, aes(x = Exercise, y = Exercise.Intensity, fill = BMI.Classification)) +
  geom_boxplot(position = position_dodge(width = 0.8)) +
  labs(title = "Exercise Intensity by BMI Classification", x = "Exercise", y = "Exercise Intensity") +
  scale_fill_manual(values = c(
    "Underweight" = "yellow",
    "Overweight" = "red",
    "Obesity" = "green",
    "Healthy weight" = "blue"
  )) +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))

# Display the bar plot
print(bar_plot)

# Display the box plot
print(box_plot)

```

different visualization

```{r}
df_summary <- df %>%
  group_by(Exercise, Gender) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = Gender)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c( "pink","lightblue")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender", fill = "Gender", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

```{r}
library(dplyr)
# Calculate the count and frequency of BMI classifications by Exercise, Gender
df_summary <- df %>%
  group_by(Exercise, Gender, BMI.Classification) %>%
  summarise(count = n()) %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = BMI.Classification)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("Overweight" = "red", "Obesity" = "green", "Healthy weight" = "blue")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and BMI Classification", fill = "BMI Classification", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

## Analysis by Calories burn and Exercise Intensity

Q)  How do age, actual weight, and duration collectively influence the relationship between exercise intensity and calorie burn?

```{r Smart Question 1}
library(ggplot2)
ggplot(df, aes(x=Age, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Age on Exercise Intensity and Calorie Burn") +
  xlab("Age") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

ggplot(df, aes(x=Actual.Weight, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Actual Weight on Exercise Intensity and Calorie Burn") +
  xlab("Actual Weight") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

ggplot(df, aes(x=Duration, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Duration on Exercise Intensity and Calorie Burn") +
  xlab("Duration") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

```

```{r}
# Create a scatterplot to visualize the relationship between Age, Duration, and Calories.Burn
library(ggplot2)

scatterplot <- ggplot(df, aes(x = Age, y = Duration, color = Calories.Burn)) +
  geom_point() +
  labs(title = "Relationship between Age, Duration, and Calorie Burn", x = "Age", y = "Duration") +
  scale_color_gradient(low = "blue", high = "red") +
  theme_minimal()

print(scatterplot)

```

```{r}
exercise_calories <- ggplot(df, aes(x = Intensity, y = Calories.Burn)) +
  geom_histogram(stat = 'identity', fill = 'blue', color = 'grey') +
  labs(title = 'Exercise Intensity vs Calories Burn', x = 'Intensity', y = 'Calories Burn') +
  theme_minimal()

print(exercise_calories)
```

```{r}
library(ggplot2)

# Calculating efficiency
df <- transform(df, Efficiency = Calories.Burn / Duration)

# Sorting the data frame by efficiency in descending order
df <- df[order(-df$Efficiency), ]

# Defining a custom color palette
my_colors <- c("Aerobics" = "blue", "Strength Training" = "green", "High Intensity Training" = "yellow","Weight Training" = "orange", "Yoga" = "red", "Basic Workout" = "purple", "Cardio" = "pink","Leg Workout" = "brown", "Circuit Training" = "gray", "Core Workout" = "cyan")

# Creating a bar plot
efficiency_plot <- ggplot(df, aes(x = Efficiency, y = reorder(Exercise, -Efficiency))) +
  geom_bar(stat = "identity", aes(fill = Exercise)) +
  scale_fill_manual(values = my_colors) +
  labs(title = "Exercise Efficiency", x = "Efficiency", y = "Exercise") +
  theme_minimal()


print(efficiency_plot)
```

```{r}
# Calculate the count and frequency of exercises by Exercise, Gender, and Intensity
df_summary <- df %>%
  group_by(Exercise, Gender, Intensity) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = Intensity)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("red", "green", "blue", "purple", "orange", "pink", "yellow")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and intensity", fill = "Intensity", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

### Analysis by Weather

Q)  Are there exercises that are more commonly performed indoors or outdoors depending on the weather?

```{r Smart Question 4}
ggplot(df, aes(x=Exercise, fill=Weather.Conditions)) +
  geom_bar() +
  ggtitle("Exercises by Weather Conditions")

```

```{r}
# Calculate the count and frequency of exercises by Exercise, Gender, and Weather Conditions
df_summary <- df %>%
  group_by(Exercise, Gender, Weather.Conditions) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = Weather.Conditions)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("red", "green", "blue", "purple", "orange", "pink", "yellow", "cyan", "magenta", "lime")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and weather", fill = "Weather", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

```{r}

# Create a big grid of scatter plots with facets for Exercise and Weather Conditions
scatter_grid <- ggplot(df, aes(x = Duration, y = `Exercise.Intensity`)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +  # Add a line of best fit
  facet_grid(Exercise ~ `Weather.Conditions`) +
  labs(title = "Relationship between weather and exercise", x = "Duration", y = "Exercise Intensity") +
  theme_minimal()+
  theme(axis.text.y = element_blank())

# Display the big grid of plots
print(scatter_grid)

```

📌As you can see, the intensity and duration of training in some exercises depends on the weather.

## Analysis by Gender

Q)  Do males and females exhibit different patterns in terms of exercise variety?

```{r Smart Question 3}
library(ggplot2)

# Create the bar plot
bar_plot <- ggplot(df, aes(x = Exercise, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1)) +
  ggtitle("Exercise Variety by Gender")

# Display the plot
print(bar_plot)

```

```{r}
library(ggplot2)
library(viridis)  # Load the viridis package

# Create the box plot with the x and y axes interchanged
box_plot <- ggplot(df, aes(x = Exercise, y = BMI, fill = Gender)) +
  geom_boxplot() +
  ggtitle("Boxplot of BMI by Exercise Type and Gender") +
  theme(axis.text.x = element_text(angle = 75, hjust =1),panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white")) +
  scale_fill_viridis(discrete = TRUE)

# Display the plot
print(box_plot)

```

## Analysis by Time

Q)  Can we establish a time-based trend in the dataset, such as changes in exercise preferences over time?

```{r Smart Question 5}
ggplot(df, aes(x=factor(Duration), fill=Exercise)) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 75, hjust =1))+
  ggtitle("Exercise Preferences by Duration")

```

## Analysis by Weight

Q)  How closely do individuals' dream weights align with their actual weights?

```{r Smart Question 6}
# Create a new variable for the difference between Actual and Dream Weight
df$Weight.Diff = abs(df$Actual.Weight - df$Dream.Weight)
df$Weight.Diff.Bin = cut(df$Weight.Diff, breaks = c(0, 5, 10, 15, Inf), labels = c("0-5", "6-10", "11-15", "15+"))

# Create the scatter plot
ggplot(df, aes(x=Actual.Weight, y=Dream.Weight, color=Weight.Diff.Bin)) +
  geom_point() +
  scale_color_manual(values = c("0-5" = "blue", "6-10" = "green", "11-15" = "yellow", "15+" = "red")) +
  ggtitle("Actual Weight vs Dream Weight")
```

## Statistical Tests

Q)  Do weather conditions have a statistically significant impact on the number of calories burned during exercise?" Ans) A suitable test for this question would be Analysis of Variance (ANOVA), particularly since we have more than two weather conditions in our dataset (e.g., Sunny, Rainy, Cloudy).

**1. Data Filtering** First, lets remove any missing values for 'Weather Conditions' and 'Calories Burn'. But turns out there are no missing values in our data as we checked earlier. So we can proceed to the next step.

**2. Data Grouping** First, lets remove any missing values for 'Weather Conditions' and 'Calories Burn'. But turns out there are no missing values in our data as we checked earlier. So we can proceed to the next step.

## One Way Anova Test

### Q) Is there a significant difference in the 'Calories Burn' across different 'BMI Classification' groups?

Solution:

***Defining the Hypothesis: H0: The mean 'Calories Burn' is the same for all 'BMI Classification' groups. H1: At least one 'BMI Classification' group has a different mean 'Calories Burn'.***

```{r}
# One-Way ANOVA
anova_result <- aov(Calories.Burn ~ BMI.Classification, data = df)
summary(anova_result)

```

```{r}
# Directly display the ANOVA summary to check p-value
anova_summary <- summary(anova_result)
print(anova_summary)

# Tukey HSD Test for Post-Hoc Analysis
posthoc <- TukeyHSD(anova_result)
print(posthoc)
```

### Interpretation:

1.  ANOVA: The p-value from the ANOVA test is 0.509, which is greater than 0.05. This means that we fail to reject the null hypothesis (H0), suggesting there is no significant difference in 'Calories Burn' across the different 'BMI Classifications' in out dataset.

2.  Post-Hoc Test: The Tukey HSD test also supports this result. All pairwise comparisons have adjusted p-values greater than 0.05, confirming that the mean 'Calories Burn' is not significantly different between any two 'BMI Classification' groups.

### Visualizations to Support ANOVA Findings

```{r}
# Load ggplot2 package
library(ggplot2)


# Create a Colorful Boxplot
ggplot(df, aes(x=BMI.Classification, y=Calories.Burn, fill=BMI.Classification)) +
  geom_boxplot() +
  scale_fill_brewer(palette="Set1") +
  theme_minimal() +
  ggtitle("Boxplot of 'Calories Burn' by 'BMI Classification'") +
  xlab("BMI Classification") +
  ylab("Calories Burn")


ggplot(df, aes(x=BMI.Classification, y=Calories.Burn, fill=BMI.Classification)) +
  geom_violin() +
  scale_fill_brewer(palette="Set3") +
  theme_minimal() +
  ggtitle("Violinplot of 'Calories Burn' by 'BMI Classification'") +
  xlab("BMI Classification") +
  ylab("Calories Burn")



ggplot(df, aes(x=BMI.Classification, y=Calories.Burn)) +
  geom_boxplot(aes(fill=BMI.Classification), alpha=0.5) +
  geom_jitter(aes(color=BMI.Classification), width=0.2) + 
  ggtitle("Boxplot and Swarmplot of 'Calories Burn' by 'BMI Classification'") +
  xlab("BMI Classification") +
  ylab("Calories Burn")

```

1.  Boxplot: The boxplot shows the median, quartiles, and outliers for 'Calories Burn' for each 'BMI Classification'. The overlap of the interquartile ranges suggests that there's no significant difference in 'Calories Burn' across the groups.

2.  Violinplot: The violinplot combines a boxplot with a kernel density estimation. It provides more information about the density of the data points at different calorie levels. Again, the shapes of the "violins" are quite similar for all categories, indicating no significant difference in 'Calories Burn'.

3.  Boxplot and Swarmplot: The swarmplot overlay on the boxplot displays individual data points, sampled to avoid clutter. This provides a sense of the data distribution while still summarizing it with a boxplot. Once more, the distribution of points appears quite similar across the 'BMI Classification' groups.

### Correlation

```{r}
df$Gender <- as.factor(df$Gender)
df$BMI.Classification <- as.factor(df$BMI.Classification)
df$Weather.Conditions <- as.factor(df$Weather.Conditions)
df$Intensity <- as.factor(df$Intensity)
df$Duration <- as.numeric(df$Duration)
```

```{r}
# Identify the numeric columns
numeric_columns <- sapply(df, is.numeric)

# Calculate the correlation matrix for numeric variables
correlation <- cor(df[, numeric_columns], use = "complete.obs")
```

```{r}
correlation <- correlation[-which(rownames(correlation) == "ID"), -which(colnames(correlation) == "ID")]

library(corrplot)

# Create the correlation heatmap
corrplot(correlation, method = "color", type = "upper", tl.col = "black", tl.srt = 45, 
         diag = FALSE, addCoef.col = "black", tl.cex = 0.7)

# Add a title
title("Correlation Heatmap")
```

### Linear Model

```{r}
linear_model <- lm(Calories.Burn ~ Efficiency + Duration, data = df)

# Summarize the model
summary(linear_model)
```

The linear regression model aims to predict "Calories Burn" based on two predictor variables: "Efficiency" and "Duration." Here are some observations based on the model's summary:

1.  **Model Fit**: The model provides a good fit for the data, with an adjusted R-squared value of 0.8515. This indicates that approximately 85.15% of the variance in "Calories Burn" is explained by the predictors, "Efficiency" and "Duration."

2.  **Significant Predictors**: Both predictor variables, "Efficiency" and "Duration," are statistically significant in predicting "Calories Burn." The p-values associated with these predictors are very close to zero, suggesting a strong relationship between the predictors and the target variable.

3.  **Intercept**: The intercept term (-233.63370) represents the estimated "Calories Burn" when both "Efficiency" and "Duration" are zero. While this value may not have a practical interpretation in this context, it's essential for the model's calculations.

4.  **Coefficients**: The coefficients for the predictor variables provide insights into the relationship between each predictor and the target variable.

    -   For "Efficiency," a one-unit increase results in an estimated increase of approximately 31 calories burned.
    -   For "Duration," a one-minute increase results in an estimated increase of approximately 7 calories burned.

5.  **Residuals**: The residuals indicate the model's prediction errors. The residuals are relatively symmetrically distributed around zero, suggesting that the model's assumptions about errors are reasonably met.

6.  **F-Statistic**: The F-statistic tests whether the overall model is a good fit for the data. With a very high F-statistic and an associated p-value close to zero, it suggests that the model as a whole is a good fit.

7.  **Residual Standard Error**: The residual standard error of 44.64 provides a measure of the typical prediction error of the model. Smaller values indicate better model fit.

In summary, this linear regression model is highly significant and explains a substantial portion of the variance in "Calories Burn." Both "Efficiency" and "Duration" are strong predictors of calorie burn, with efficiency having the most substantial effect. However, it's essential to remember that regression models imply association, and they don't establish causation. Other factors not included in the model could also influence calorie burn.

### Final Takeaway:

Based on these results, we can conclude that our initial hypothesis, which was to find out if there is a significant difference in 'Calories Burn' across 'BMI Classification' groups, is not supported by the data. Both the ANOVA and the post-hoc Tukey HSD test indicate that there are no significant differences in the 'Calories Burn' among the different 'BMI Classification' categories. Furthermore, all these visualizations reinforce the ANOVA findings that there is no significant difference in the 'Calories Burn' across different 'BMI Classification' categories.
