---
title: "Final_Yash"
output: html_document
date: "2023-10-23"
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installing Required Packages
```{r Packages}
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("corrplot")

library(ggplot2)
library(dplyr)
library(corrplot)

```

## Data Preprocessing  
For the data preprocessing part, we will do three things for now: 
1. Load the Dataset
2. Check for Missing Values
3. Check Variable Datatypes & Typecast if necessary


```{r Loading dataset}
#setwd = "C:\\Users\\YASH KATTIMANI\\Downloads"
df = read.csv("newexercise_dataset.csv")
str(df)
```

```{r Check for Missing Values}
null_values <- sum(is.na(df))
print(null_values)
```
Turns out there are 0 null values, so we can go ahead without having to worry about this aspect. 

```{r Typecasting}
#converting exercise from char to factor
df$Exercise = as.factor(df$Exercise)
```

## Deep Dataset Analysis

Frequency of different Exercises
```{r Frequency of different Exercises}
library(ggplot2)
exercise_count <- ggplot(df,aes(x= Exercise,fill = Exercise))+
  geom_bar()+
  labs(title ="Distribution of Exercise", x = "Exercise", y = "Count" )+
  theme(axis.text.x = element_text(angle = 75,hjust = 1))+
  scale_fill_manual(values = rainbow(length(unique(df$Exercise))))
print(exercise_count)
```

Classification of BMI values to 4 different categories

```{r Classification of BMI values to 4 categories}
# Creating a new variable BMI.Classification based on BMI values
df$BMI.Classification <- ifelse(df$BMI < 18.5, "Underweight",
                                ifelse(df$BMI < 25, "Healthy weight",
                                       ifelse(df$BMI < 30, "Overweight", "Obesity")))

head(df)
```

```{r Plot for classification of BMI values to 4 categories}
bmi_bar_plot <- ggplot(df, aes(x = BMI.Classification, fill = BMI.Classification)) +
  geom_bar() +
  labs(title = "BMI Classification", x = "Classification", y = "Count") +
  scale_fill_manual(values = c(
    "Underweight" = "red",
    "Healthy weight" = "green",
    "Overweight" = "yellow",
    "Obesity" = "orange"
  )) +
  theme_minimal()

print(bmi_bar_plot)
```

Classification of Levels of Intensity based on Intensity values

```{r Classification of Levels of Intensity}
# Creating a new variable 'Intensity' based on Exercise.Intensity values
df$Intensity <- ifelse(df$Exercise.Intensity < 3, "Low Intensity",
                      ifelse(df$Exercise.Intensity < 6, "Medium Intensity", "High Intensity"))

# View the first few rows of the updated dataframe to verify the new variable
head(df)
```

Converting Heart rate to different levels "Low", "Moderate", "Elevated", "High", "Very High"

```{r Converting Heart rate to different levels}
breaks <- c(0, 100, 120, 140, 160, Inf)  # Customizing the breaks requirements
labels <- c("Low", "Moderate", "Elevated", "High", "Very High")

# Use the cut function to categorize Heart Rate into levels
df$HeartRateLevel <- cut(df$Heart.Rate, breaks = breaks, labels = labels, right = FALSE)
```

## Analysis of Age

📌Age analysis shows that men are more active until the age of 28, then women dominate. In addition, there are a large number of people over the age of 60.

```{r}
# Create a density plot with KDE
density_plot <- ggplot(df, aes(x = Age, fill = Gender, color = Gender)) +
  geom_density(alpha = 0.5) +
  labs(title = "Age distribution", x = "Age") +
  theme_minimal() +
  scale_fill_manual(values = c("blue", "red")) +
  scale_color_manual(values = c("blue", "red"))

print(density_plot)
```

```{r}
hist(df$Age, main = "Distribution of Age", xlab = "Age", ylab = "Count", col = "lightblue")
```

### Analysis of BMI

Q) Can the combination of heart rate and BMI be used to determine the optimal exercise duration for achieving dream weight?
```{r Smart Question 2}
ggplot(df, aes(y=Heart.Rate, x=BMI, color= BMI.Classification)) +
  geom_point() +
  ggtitle("Heart Rate and BMI vs Exercise Duration for Achieving Dream Weight")
```

```{r}
bmi_bar_plot <- ggplot(df, aes(x = BMI.Classification, fill = BMI.Classification)) +
  geom_bar() +
  labs(title = "BMI Classification", x = "Classification", y = "Count") +
  scale_fill_manual(values = c(
    "Underweight" = "red",
    "Healthy weight" = "green",
    "Overweight" = "yellow",
    "Obesity" = "orange"
  )) +
  theme_minimal()

print(bmi_bar_plot)
```

```{r}
# Calculating the distribution of BMI classifications
bmi_class_counts <- table(df$BMI.Classification)

# Calculating the percentages
bmi_class_percentages <- prop.table(bmi_class_counts) * 100

# Create a pie chart
pie(bmi_class_counts, labels = paste(names(bmi_class_counts), "(", round(bmi_class_percentages, 1), "%)"), col = c("red", "green", "blue"))
title("Distribution by BMI Classification")
```

```{r}
countplot <- ggplot(df, aes(x = Exercise, fill = BMI.Classification)) +
  geom_bar(position = "dodge") +
  labs(title = "Exercise by BMI Classification", x = "Exercise", y = "Count") +
  scale_fill_manual(values = c("Underweight" = "yellow","Overweight" = "red", "Obesity" = "green", "Healthy weight" = "blue")) +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))

print(countplot)

```

different visualization

```{r}
library(dplyr)
# Calculate the count and frequency of BMI classifications by Exercise, Gender
df_summary <- df %>%
  group_by(Exercise, Gender, BMI.Classification) %>%
  summarise(count = n()) %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = BMI.Classification)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("Overweight" = "red", "Obesity" = "green", "Healthy weight" = "blue")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and BMI Classification", fill = "BMI Classification", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

## Analysis by Calories burn and Exercise Intensity

Q) How do age, actual weight, and duration collectively influence the relationship between exercise intensity and calorie burn?
```{r Smart Question 1}
library(ggplot2)
ggplot(df, aes(x=Age, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Age on Exercise Intensity and Calorie Burn") +
  xlab("Age") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

ggplot(df, aes(x=Actual.Weight, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Actual Weight on Exercise Intensity and Calorie Burn") +
  xlab("Actual Weight") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

ggplot(df, aes(x=Duration, y=Calories.Burn, color=Exercise.Intensity)) +
  geom_point() +
  ggtitle("Influence of Duration on Exercise Intensity and Calorie Burn") +
  xlab("Duration") +
  ylab("Calories Burnt") +
  theme(panel.background = element_rect(fill = "white"))

```


```{r}
exercise_calories <- ggplot(df, aes(x = Intensity, y = Calories.Burn)) +
  geom_histogram(stat = 'identity', fill = 'blue', color = 'grey') +
  labs(title = 'Exercise Intensity vs Calories Burn', x = 'Intensity', y = 'Calories Burn') +
  theme_minimal()

print(exercise_calories)
```

```{r}
library(ggplot2)

# Calculating efficiency
df <- transform(df, Efficiency = Calories.Burn / Duration)

# Sorting the data frame by efficiency in descending order
df <- df[order(-df$Efficiency), ]

# Defining a custom color palette
my_colors <- c("Aerobics" = "blue", "Strength Training" = "green", "High Intensity Training" = "yellow","Weight Training" = "orange", "Yoga" = "red", "Basic Workout" = "purple", "Cardio" = "pink","Leg Workout" = "brown", "Circuit Training" = "gray", "Core Workout" = "cyan")

# Creating a bar plot
efficiency_plot <- ggplot(df, aes(x = Efficiency, y = reorder(Exercise, -Efficiency))) +
  geom_bar(stat = "identity", aes(fill = Exercise)) +
  scale_fill_manual(values = my_colors) +
  labs(title = "Exercise Efficiency", x = "Efficiency", y = "Exercise") +
  theme_minimal()


print(efficiency_plot)
```

```{r}
# Calculate the count and frequency of exercises by Exercise, Gender, and Intensity
df_summary <- df %>%
  group_by(Exercise, Gender, Intensity) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = Intensity)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("red", "green", "blue", "purple", "orange", "pink", "yellow")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and intensity", fill = "Intensity", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

### Analysis by Weather 

Q) Are there exercises that are more commonly performed indoors or outdoors depending on the weather?
```{r Smart Question 4}
ggplot(df, aes(y=Exercise, fill=Weather.Conditions)) +
  geom_bar() +
  ggtitle("Exercises by Weather Conditions")

```

```{r}
# Calculate the count and frequency of exercises by Exercise, Gender, and Weather Conditions
df_summary <- df %>%
  group_by(Exercise, Gender, Weather.Conditions) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(frequency = count * 100 / sum(count))

# Create a grouped bar plot
grouped_bar_plot <- ggplot(df_summary, aes(x = Gender, y = frequency, fill = Weather.Conditions)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = c("red", "green", "blue", "purple", "orange", "pink", "yellow", "cyan", "magenta", "lime")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  facet_wrap(~Exercise) +
  theme_light() +
  labs(title = "(%) of exercises by gender and weather", fill = "Weather", x = "", y = "") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = "top")

# Display the grouped bar plot
print(grouped_bar_plot)
```

```{r}

# Create a big grid of scatter plots with facets for Exercise and Weather Conditions
scatter_grid <- ggplot(df, aes(x = Duration, y = `Exercise.Intensity`)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +  # Add a line of best fit
  facet_grid(Exercise ~ `Weather.Conditions`) +
  labs(title = "Relationship between weather and exercise", x = "Duration", y = "Exercise Intensity") +
  theme_minimal()+
  theme(axis.text.y = element_blank())

# Display the big grid of plots
print(scatter_grid)

```

## Analysis by Gender
Q) Do males and females exhibit different patterns in terms of exercise variety?
```{r Smart Question 3}
ggplot(df, aes(y=Exercise, fill=Gender)) +
  geom_bar(position="dodge") +
  ggtitle("Exercise Variety by Gender")
```

```{r}
# Boxplot of BMI by Exercise Type and Gender
ggplot(df, aes(y=Exercise, x=BMI, fill=Gender)) +
  geom_boxplot() +
  ggtitle("Boxplot of BMI by Exercise Type and Gender") +
  theme(panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"))+
        scale_fill_viridis(discrete=TRUE)

```

## Analysis by Time 

Q) Can we establish a time-based trend in the dataset, such as changes in exercise preferences over time?
```{r Smart Question 5}
ggplot(df, aes(y=factor(Duration), fill=Exercise)) +
  geom_bar() +
  ggtitle("Exercise Preferences by Duration")

```

## Analysis by Weight

Q) How closely do individuals' dream weights align with their actual weights?
```{r Smart Question 6}
# Create a new variable for the difference between Actual and Dream Weight
df$Weight.Diff = abs(df$Actual.Weight - df$Dream.Weight)
df$Weight.Diff.Bin = cut(df$Weight.Diff, breaks = c(0, 5, 10, 15, Inf), labels = c("0-5", "6-10", "11-15", "15+"))

# Create the scatter plot
ggplot(df, aes(x=Actual.Weight, y=Dream.Weight, color=Weight.Diff.Bin)) +
  geom_point() +
  scale_color_manual(values = c("0-5" = "blue", "6-10" = "green", "11-15" = "yellow", "15+" = "red")) +
  ggtitle("Actual Weight vs Dream Weight")
```